The complex structure and peculiar internal motions of the planetary nebula NGC 6210

### 2020-05-15 ms.tex
Re-do the halo knot figure

\begin{figure*}
\centering
  \includegraphics[width=1\textwidth]{tere-figs/Figure3}
  \caption{ }
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.4\textwidth]{tere-figs/Figure6}
  \caption{  }
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=1\textwidth]{tere-figs/Figure3}
  \caption{}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/turtle-halo-slit-x}
  \caption{
    Deep images and spectra of the outer halo of NGC~6210, showing knotty structure.
    (a)~Composite mosaic of \oiii{} images,
    each with an exposure time of 1800~s,
    giving a combined field of view of \(3' \times 3'\) centered on the nebula.
    The position of slit position X is shown, for which a deep \Ha{} spectrum was obtained.
    Note that different sections of the mosaic are shown with different brightness normalizations,
    leading to abrupt jumps at the boundaries. 
    (b)~\Ha{} spectrum from Slit~X, showing emission from two of the halo knots.
    The red dotted line shows the nebular systemic velocity.
  }
  \label{fig:halo-knots}
\end{figure}
